Local PCA results

### 2016-05-28 medicago/summarize_run.Rmd
different sort of querying function

Now, we'll look at PCA plots from the extracted corners.
(warning: takes awhile and a lot of RAM)
```{r corner_pca, cache=TRUE}
corner.npc <- 4
corner.regions <- lapply( 1:ncol(mds.corners), function (k) {
            regions[ mds.corners[,k], ]
    } )
corner.pca <- lapply( corner.regions, function (reg) {
            geno <- vcf_multi_query( chrom.list=chroms, file=bcf.files, regions=reg )
            cov_pca(geno,k=corner.npc,w=opt$weights)
    } )
```

>>>>

Now, we'll look at PCA plots from the extracted corners.
(warning: takes awhile and a lot of RAM)
```{r corner_pca, cache=TRUE}
corner.npc <- 4
corner.regions <- lapply( 1:ncol(mds.corners), function (k) {
            regions[ mds.corners[,k], ]
    } )
corner.pca <- lapply( corner.regions, function (reg) {
            geno <- multi_vcf_query( chrom.list=chroms, file=bcf.files, regions=reg )
            cov_pca(geno,k=corner.npc,w=opt$weights)
    } )
```
